# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
## Loading and preprocessing the data
```{r}
unzip("activity.zip")
activity <- read.csv("activity.csv")
```


## What is mean total number of steps taken per day?
1. Make a histogram of the total number of steps taken each day
```{r}
steps.date <- aggregate(steps ~ date, data=activity, FUN=sum)
hist(steps.date$steps,xlab="total amounts", ylab="frequencies")
```
2. Calculate and report the **mean** and **median** total number of
   steps taken per day

```{r}
mean(steps.date$steps)
median(steps.date$steps)
```
## What is the average daily activity pattern?
1. Make a time series plot (i.e. `type = "l"`) of the 5-minute
   interval (x-axis) and the average number of steps taken, averaged
   across all days (y-axis)

```{r}
steps.interval <- aggregate(steps ~ interval, data=activity, FUN=mean)
plot(steps.interval, type="l")
```

2. Which 5-minute interval, on average across all the days in the
   dataset, contains the maximum number of steps?

```{r}
steps.interval$interval[which.max(steps.interval$steps)]
```



## Imputing missing values
1. Calculate and report the total number of missing values in the
   dataset (i.e. the total number of rows with `NA`s)

```{r}
sum(is.na(activity))
```


## Are there differences in activity patterns between weekdays and weekends?
